### 2015-01-13 paper/Content/01introduction.tex
typos

\IEEEPARstart{T}{he \emph{Android}} operating system is one of the most 
commonly used in mobile industry. After its first presentation in 2007, the open source system started its successful journey and became the leading mobile operating system in 2010 \cite{PassiveMVC}. According to Gartner \cite{GartnerAndroid2015}, there will be over 1.4 billion \emph{Android}-based devices sold in 2015.

@@

In the next section we shortly show what core components, provided by the \emph{Android} SDK, need to be considered for our MVP implementation. In addition, we elaborate what types of \emph{Model-View-Presenter} approaches exist and which one we have chosen to build our app prototype. This is followed by an detailed explanation how we applied MVP to the Android SDK and how we built our app prototype. The last section concludes our findings.

>>>>

\IEEEPARstart{T}{he \emph{Android}} operating system is one of the most 
commonly used in mobile industry. After its first presentation in 2007, the open source system started its successful journey and became the leading mobile operating system in 2010 \cite{PassiveMVC}. According to Gartner \cite{GartnerAndroid2015}, there will be over 1.4 billion \emph{Android}-based devices sold in 2015.\\

@@

In the next section we shortly show what core components, provided by the \emph{Android} SDK, need to be considered for our MVP implementation. In addition, we elaborate what types of \emph{Model-View-Presenter} approaches exist and which one we have chosen to build our app prototype. This is followed by a detailed explanation how we applied MVP to the Android SDK and how we built our app prototype. The last section concludes our findings.

### 2015-01-13 paper/Content/abstract.tex

\begin{abstract}
%\boldmath
The abstract goes here.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Android, Research, SWA, MVP, MVC, Kraut, R\"uben.
\end{IEEEkeywords}

>>>>

\begin{abstract}
%\boldmath
Today, \emph{Android} is the most commonly used operating system in mobile industry. It allows a wide variety of architecture approaches in application development, all having their own advantages and disadvantages regarding testability, maintainability and the like. 
After introducing the basic components of \emph{Android} applications and giving an overview about the current state in \emph{Android} development, this paper describes how the Model-View-Presenter (MVP) approach can be used to develop applications that can be conveniently tested, maintained and extended.
To support the idea presented in this paper, an Android app called \emph{Yet Another Weather App} is created using the methods described in the paper.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Android,  Application Architecture, Model-View-Presenter (MVP), App Prototype.
\end{IEEEkeywords}
